A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-09-04 rr-flow.Rmd
declare files as bash, so they get wrapped

```
target: dependency1 dependency2
  command-to-create-target
```

@@

```
analysis.pdf: data/clean.csv
  Rscript -e 'rmarkdown::render("analysis.Rmd")'

@@

```
all: analysis.pdf
```

@@

```
FROM rocker/verse:3.6.1
RUN install2.r --error --skipinstalled\
  pacman here pander
RUN installGithub.r\
  crsh/papaja benmarwick/wordcountaddin
WORKDIR /home/rstudio
```

@@

```
projekt := $(shell basename `git rev-parse --show-toplevel`)
current_dir := $(shell pwd)
uid = $(shell id -u)

>>>>

```{bash, eval=FALSE}
target: dependency1 dependency2
  command-to-create-target
```

@@

```{bash, eval=FALSE}
analysis.pdf: data/clean.csv
  Rscript -e 'rmarkdown::render("analysis.Rmd")'

@@

```{bash, eval=FALSE}
all: analysis.pdf
```

@@

```{bash, eval=FALSE}
FROM rocker/verse:3.6.1
RUN install2.r --error --skipinstalled\
  pacman here pander
RUN installGithub.r\
  crsh/papaja benmarwick/wordcountaddin
WORKDIR /home/rstudio
```

@@

```{bash, eval=FALSE}
projekt := $(shell basename `git rev-parse --show-toplevel`)
current_dir := $(shell pwd)
uid = $(shell id -u)
